---
title: "Replication of BCXL"
author: "Shunsuke Matsuno"
date: "2020/6/1"
output:
  prettydoc::html_pretty:
    theme: cayman
    highlight: github
---

```{r settings, echo=FALSE}
### Setting the global code chunk options ###
# Args
#   comment='': won't append any string to the start of each line of results
#   fig.align='center': align figures to the center of document
knitr::opts_chunk$set(comment="", fig.align="center", warning = FALSE)
```

# Description


# Required libraries
```{r, message=FALSE}
easypackages::libraries('tidyverse', 'ggplot2', 'BCXL')
```

# Simulate Data
- In this section, we simulate data according to the optimization behavior described in the paper and estimated parameters.

## Parameters
- I use pre-SOX parameters
```{r}
theta_inv <- 1/0.007
m         <- -0.011
sigma     <- 0.031

theta <- c(theta_inv = theta_inv, m = m, sigma = sigma)
```

## Optimization
- The investor's pricing function is written in `investor_response.R`.
```{r}
r <- seq(-0.1, 0.1, .0005)
price <- investor_response(r)
qplot(r, price, geom = 'line') + 
  geom_vline(xintercept = 0, linetype = 'dotted') +
  geom_hline(yintercept = 0, linetype = 'dotted') +
  theme_bw()
```

## Private Signal

```{r}
set.seed(1)

N <- 100000    # the number of firms

df_firm <- tibble(
  firm = 1:N,
  x = rnorm(N, m, sigma)
  )

ggplot(df_firm, aes(x = x)) +
  geom_histogram(color="white", bins = 50) +
  theme_bw()
```

- Then, I simulate optimal reporting.
- The cost function is specified as quadratic: 

$$
  \psi(r-x) = 2 (r-x)^2
$$
- `compute_optimal_reporting.R` computes the optimal manipulation.
    - This function depentds on `compute_utility.R`, which computes the utility for each manipulation and $x$.
    - Please see `Summary of BCXL.pdf` and the original paper for more details.
```{r}
compute_utility
compute_optimal_reporting
```

```{r}
# optimal reporting
df_firm_reported <- df_firm %>% 
  mutate(r = map_dbl(.x = x, .f = compute_optimal_reporting, theta = theta)) %>% 
  mutate(price = investor_response(r))

# plot
df_firm_reported_plot <- df_firm_reported %>% 
  select(firm, x, r) %>% 
  pivot_longer(-firm, names_to = "type", values_to = "freq")

ggplot(df_firm_reported_plot, aes(x = freq, fill = type)) +
  geom_histogram(aes(y = ..density..),
                 color    = 'white',
                 position = 'identity', 
                 alpha    = .5,
                 bins     = 50) +
  theme_bw()
```
- I regard the simulated reporting as 'observed' data.

### Cost parameter
- By the way, we can play around by changing the values of $\theta^-1$ to see the effect on reported distribution.
    - We expect the the distribution of $x$ and $r$ is close when $\theta^-1$ is small and vice versa.
    - `plot_r_x.R` is the function that takes $\theta^01$ and re-computes the code.
```{r}
# low cost
plot_r_x(1/2 * theta[1])

# high cost
plot_r_x(2* theta[1])
```


# Estimation

## Step 1. Estimation of pricing strategy
- I use polynomial regression to estimate $\gamma$.
    - `estimate_gamma_poly.R` computes predicted value of price with polynomial specification and derive its first- and second-order derivatives analytically.
```{r}
estimate_gamma_poly
```
  

## Step 2. Parameter Search
- `compue_lkhd.R` returns negative likelihood.
```{r}
compute_lkhd
```

- We minimizes this negative likelihood.

```{r}
# optimization
optim_result <- optim(par    = theta,
                      fn     = compute_lkhd,
                      df     = df_firm_reported,
                      lower  = c(0.00001, -5, 0.00001),
                      upper  = c(1000, 5, 10),
                      method = "L-BFGS-B"
                      )
optim_result
```
## Plot objective function
- We see the values of objective functions around the true parameter values.
    - `plot_obj.R` does this.
```{r}
plot_obj
```

```{r plot, cache=TRUE}
theta_inv_vec <- seq(100, 200, 2)
plot_obj(theta, df_firm_reported, theta_inv_vec, 1)

m_vec <- seq(-1, 1, .05)
plot_obj(theta, df_firm_reported, m_vec, 2)

sigma_vec <- seq(0.01, .1, .002)
plot_obj(theta, df_firm_reported, sigma_vec, 3)
```

